### 2016-03-10 manuscript.Rnw
add that API versions can be selected
add mention of trait databases

\texttt{rotl} gives users access to all endpoints provided by version 2 of the
OTL APIs. Phylogenetic trees served by the API can be imported directly into
R's memory and are represented using the \texttt{ape} \citep{Paradis2004} tree
structure (objects of class \texttt{phylo}), or can be written to files in the
Newick, NEXUS \citep{Maddison1997}, or NeXML \citep{Vos2012} file formats. This
allows researchers to use these trees either directly with other R packages, or
to be imported in other programs that make use of phylogenetic tree files.

@@

>>>>

\texttt{rotl} gives users access to all endpoints provided by version 2 of the
OTL APIs, and other versions of the API can be selected by the user as they
become available. Phylogenetic trees served by the API can be imported directly into
R's memory and are represented using the \texttt{ape} \citep{Paradis2004} tree
structure (objects of class \texttt{phylo}), or can be written to files in the
Newick, NEXUS \citep{Maddison1997}, or NeXML \citep{Vos2012} file formats. This
allows researchers to use these trees either directly with other R packages, or
to be imported in other programs that make use of phylogenetic tree files.

@@

As trait databases are becoming increasingly more common, and interfaces to the
data they contains are being developed as R packages \citep[e.g., the package
\texttt{traits}][]{Chamberlain2015}, \texttt{rotl} provides a
way to easily retrieve phylogenetic information for species trait data that are available.
